
\documentclass[oneside,a4paper]{book}
%\pagestyle{headings}

\input{preamble}

% A B S T R A C T
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\chapter*{\centering Abstract}
\begin{quotation}
\noindent
The main goal of this project is to evaluate the application of \gls{dl} models for the classification of syllable types in recordings from the pups of the neotropical greater sac-winged bat (\emph{Saccopteryx bilineata}).
To realise this, two experiments were conducted, with the first one demonstrating how it is feasible and the second one presenting an actual realization of a prototype of an automated syllable type classification pipeline.

We aimed to classify the different syllable types of the adult territorial song and one variable juvenile syllable within variable vocal practice sequences. This was worked out in a supervised machine learning framework, where we investigated the effect of different preprocessing variants in combination with the features as spectrograms or \gls{hog}.
For the models, we considered different types and different constellations of artificial neural networks (recurrent, convolution and densely connected).

Our findings are promising and show that it is feasible to create an automated syllable type classification application in the given objective, although the syllables of the juveniles show a high degree of intra- and interindividudal variability because they mirror developmental and learning processes throughout ontogeny.
\end{quotation}
\clearpage

% Acknowledgements
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\chapter*{\centering Acknowledgements}
\begin{quotation}
\noindent
I would like to express my gratitude to Ahana Aurora Fernandez for providing the labelled dataset and the hours of discussion and more that formed the basis for conducting these experiments.
For their support and patience with me, I sincerely thank my supervisors Andreas Fischer and Daniel Wegman.
Thanks also to Petar Veličković, as many of the schemes on neural networks are modified versions of his publicly available work, his \href{https://github.com/PetarV-/TikZ}{TiKZ GitHub repository} was a little treasure for me.
And for providing a \gls{gpu} cluster, I would like to thanks the HPC team of UBELIX (http://www.id.unibe.ch/hpc), the high-performance computing cluster at the University of Bern, Switzerland.
And finally, I would like to thanks my friends Anna, Bettina and Sophie who all proofread my thesis.
\end{quotation}
\clearpage
\glsresetall

% C O N T E N T S
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\tableofcontents

\include{chapter/Introduction}
\newpage{\pagestyle{empty} \cleardoublepage}


\include{chapter/Background}
\newpage{\pagestyle{empty} \cleardoublepage}

\include{chapter/Datasets}
\newpage{\pagestyle{empty} \cleardoublepage}

\include{chapter/Method}
\newpage{\pagestyle{empty} \cleardoublepage}


\include{chapter/Experiments}
\newpage{\pagestyle{empty} \cleardoublepage}


\include{chapter/Conclusions}
\newpage{\pagestyle{empty} \cleardoublepage}

\begin{appendix}
\include{chapter/appendix}
\newpage{\pagestyle{empty} \cleardoublepage}
\end{appendix}
\addcontentsline{toc}{chapter}{\numberline{}List of Models}
\begin{refcontext}[sorting=none]{}
    \printbibliography[title={Models}, type=model, env=model]
\end{refcontext}
\addcontentsline{toc}{chapter}{\numberline{}List of Tables}
\listoftables
\addcontentsline{toc}{chapter}{\numberline{}List of Figures}
\listoffigures
\glsaddall
\printacronyms[title=List of Acronyms]
\addcontentsline{toc}{chapter}{\numberline{}List of Acronyms}
\addcontentsline{toc}{chapter}{\numberline{}Bibliography}
%\nocite{*}
\printbibliography[nottype=model]

% \cleardoublepage
% \pagestyle{empty}
% \begin{figure}
% \centering
% \includepdf[pages=-,offset=11mm 11mm]{MSc_masterarbeit_erklaerung_eRSL18_eng_signed.pdf}
% \end{figure}

%END Doc
%-------------------------------------------------------

\end{document}
